### 2024-10-25 machine-learning.qmd
Built site for gh-pages

>>>>

## Types of Machine Learning {#sec-machineLearningTypes}

There are many approaches to machine learning.
This chapter discusses several key ones:

- supervised learning
    - continuous outcome (i.e., regression)
      - linear regression
      - lasso regression
      - ridge regression
      - elastic net regression
    - categorical outcome (i.e., classification)
      - logistic regression
      - support vector machine
      - random forest
      - extreme gradient boosting
- unsupervised learning
    - clustering
    - principal component analysis
- semi-supervised learning
- reinforcement learning
    - deep learning

### Supervised Learning {#sec-machineLearningTypesSupervised}

[DEFINE SUPERVISED LEARNING]

Unlike linear and logistic regression, various machine learning techniques can handle multicollinearity, including LASSO regression, ridge regression, and elastic net regression.
Least absolute shrinkage and selection operator (LASSO) regression helps perform selection of which predictor variables to keep in the model by shrinking some coefficients to zero.
Ridge regression shrinks the coefficients of predictor variables toward zero, but not to zero, so it does not perform selection of which predictor variables to retain; this allows it to allow nonzero coefficients for multiple correlated predictor variables in the context of multicollinearity.
Elastic net involves a combination of LASSO and ridge regression; it performs selection of which predictor variables to keep by shrinking the coefficients of some predictor variables to zero, and it shrinks the coefficients of some predictor variables toward zero, to address multicollinearity.

Unless interactions or nonlinear terms are specified, linear, logistic, LASSO, ridge, and elastic net regresstion do not account for interactions among the predictor variables or for nonlinear associations between the predictor variables and the outcome variable.
By contrast, random forests and extreme gradient boosting do account for interactions among the predictor variables and for nonlinear associations between the predictor variables and the outcome variable.

### Unsupervised Learning {#sec-machineLearningTypesUnsupervised}

[DEFINE UNSUPERVISED LEARNING]

We describe [cluster analysis](#sec-clusterAnalysis) in @sec-clusterAnalysis.
We describe [principal component analysis](#sec-pca) in @sec-pca.

### Semi-supervised Learning {#sec-machineLearningTypesSemisupervised}

[DEFINE SEMI-SUPERVISED LEARNING]

### Reinforcement Learning {#sec-machineLearningTypesReinforcement}

[DEFINE REINFORCEMENT LEARNING]
